

\documentclass[11pt, a4paper]{awesome-cv}
\usepackage{hanging}
%\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
% Specify the location of the included fonts
\fontdir[fonts/]
\colorlet{awesome}{awesome-darknight}
 \definecolor{darktext}{HTML}{000000}
 \definecolor{text}{HTML}{000000}
 \definecolor{graytext}{HTML}{000000}
 \definecolor{lighttext}{HTML}{000000}
\setbool{acvSectionColorHighlight}{false}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}
\name{Biozid}{Bostami}
\address{Flat\# 7D, House\# 47, Road\# 11, Kallyanpur, Dhaka, Bangladesh }
\mobile{+8801625276952} 
\email{biozid0208@gmail.com}
\github{biozid-0208}
\linkedin{biozid-0208}
\stackoverflow{5539656}{biozid-bostami}
\skype{biozid.bostami} 
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}
%\quote{``Be the change that you want to see in the world."}
\renewcommand\thesection{}


\begin{document}
\makecvheader
\makecvfooter
  {}
  {Biozid Bostami}
  {\thepage}
  
\section*{Education}
\vspace{-20pt}
\noindent\makebox[\linewidth]{\rule{500pt}{1.8pt}}

\hangpara{1.5em}{1}
{\sl \textbf{Bachelor of Science }}, Computer Science \& Engineering  \hfill 2015\\
Islamic University of Technology (IUT), Gazipur, Dhaka, Bangladesh \hspace{0.2in}  GPA 3.63/4.00  \\
{\sl Thesis:} {\sl ``Performance Analysis of Caching Algorithm in Information Centric Networking"}

\hangpara{1.5em}{1}
{\sl \textbf{Higher Secondary Certificate }}, Science Group \hfill 2011\\
Dhaka College, Dhaka, Bangladesh \hspace{0.2in}  GPA 5.00/5.00  \\

\vspace*{-1em}
\hangpara{1.5em}{1}
{\sl \textbf{Secondary School Certificate }}, Science Group \hfill 2009\\
Dhanmondi Govt. Boys' High School, Dhaka, Bangladesh \hspace{0.2in}  GPA 5.00/5.00  \\

\vspace{-27pt}
\section*{Professional Experiences}
\vspace{-20pt}
\noindent\makebox[\linewidth]{\rule{500pt}{1.8pt}}

{\sl \textbf{Synesis It Limited, Dhaka, Bangladesh}\hfill August 2018$-$ Present}\\
\vspace{-17pt}
\begin{itemize}
	\item Software Developer in the projects {\sl ``Government Resource Planning"} 
	\vspace*{-.5em}
	\item Developing Micro-services architecture based product.
	\vspace*{-.5em}
	\item Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker and Jenkins.
	\vspace*{-.5em}
    \item Deployed a centralized logging environment(ELK, Filebeat) which gather log data from docker containers.
    	\vspace*{-.5em}
    \item Research with Micro-service system optimization.  
        	\vspace*{-.5em}
    \item Helping and Monitoring the junior developers.  
\end{itemize}

{\sl \textbf{WellDev Bangladesh Limited, Dhaka, Bangladesh}\hfill October 2017$-$ June 2018}\\
\vspace{-17pt}
\begin{itemize}
	\item Worked as Software Developer in several projects.
	\vspace*{-.5em}
	\item Worked with distributed System based Products
	\vspace*{-.5em}
	\item Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker and Jenkins. 
\end{itemize}

{\sl \textbf{Nascenia Limited, Dhaka, Bangladesh}\hfill June 2016$-$ September 2017}\\
\vspace{-17pt}
\begin{itemize}
	\item Worked as Jr.Software Developer in several projects.
	\vspace*{-.5em}
	\item Developed new features, Fixed bugs following the clients requirements 
	\vspace*{-.5em}
	\item Learned and Explored different Web technologies e.g: Ruby on Rails, Docker, Ansible etc. 
\end{itemize}

{\sl \textbf{Metlife Bangladesh, Dhaka, Bangladesh}\hfill February 2016$-$ May 2016}\\
\vspace{-17pt}
\begin{itemize}
	\item Worked as IT Officer.
	\vspace*{-.5em}
	\item Maintained different in-house applications.
	\vspace*{-.5em}
	\item Report and Bill generation. 
\end{itemize}

\vspace{-18pt}
\section*{Publications}
\vspace{-20pt}
\noindent\makebox[\linewidth]{\rule{500pt}{1.8pt}}

{\sl \textbf{False Data Injection Attacks in Internet of Things}\hfill    Book Chapter\\
	\vspace{-17pt}
\begin{itemize}
	\item
	Bostami B., Ahmed M., Choudhury S. (2019) False Data Injection Attacks in Internet of Things. In: Al-Turjman F. (eds) Performability in Internet of Things. EAI/Springer Innovations in Communication and Computing. Springer, Cham, \space \href{https://doi.org/10.1007/978-3-319-93557-7_4}{doi.org/10.1007/978-3-319-93557-7\_4}
		\vspace*{-.7em}
\end{itemize}

{\sl \textbf{Intrusion Detection for Big Data}\hfill    Book Chapter\\
	\vspace{-17pt}
	\begin{itemize}
		\item  Bostami, Biozid \& Ahmed, Mohiuddin. (2018). Intrusion Detection for Big Data. In: Ahmed, M. (Ed.), Pathan, A.S. (Ed.). (2019). Data Analytics. Boca Raton: CRC Press, \space \href{https://doi.org/10.1201/9780429446177-15}{doi.org/10.1201/9780429446177-15} 
		 \vspace*{-.7em}
	\end{itemize}


{\sl \textbf{Blockchain And Internet of Things}\hfill    Book Chapter\\
	\vspace{-17pt}
	\begin{itemize}
	\item Bostami, B., \& Ahmed, M. (Accepted). Blockchain And Internet of Things. In: Ahmed, M. (Ed.). Blockchain for Data Analytics. Cambridge Scholars Publishing, UK 
\end{itemize}

{\sl \textbf{Deep Learning meets Malware Detection: An Investigation}\hfill    Book Chapter\\
	\vspace{-17pt}
	\begin{itemize}
	\item Bostami, B., \& Ahmed, M. (Accepted). Deep Learning meets Malware Detection: An Investigation. In: Pathan A.S. (Ed.) ZM Fadlullah (Ed.). Combating Security Challenges in the Age of Big Data. Springer, Cham  
	\end{itemize}


\vspace{-18pt}
\section*{Professional Projects}
\vspace{-20pt}
\noindent\makebox[\linewidth]{\rule{500pt}{1.8pt}}

\hangpara{1.5em}{1}
{\sl \textbf{HelpAge}   \\
	An Application aiming to monitor and provide services to aged Rohingya people acorss the camps in Bangladesh. \\
	{\sl Technology:} {\sl Java Spring Boot \& Angular 8
			\vspace*{-.6em}	
		\begin{itemize}
			\item Currently Designing and Developing new features. 
			\vspace*{-.5em}
			\item Design and Building the backend using Spring Boot and transfer all current data from NoSql to relational database. 
			\vspace*{-.5em}
			\item Server maintenance.
		\end{itemize}
	\vspace*{-.5em}

\hangpara{1.5em}{1}
{\sl \textbf{Central Cancer Registry (CCR)}   \\
An Application aiming to collect and register all the cancer patient data across Bangladesh. \\
{\sl Technology:} {\sl Java Spring Boot \& Angular 8
		\vspace*{-.6em}	
\begin{itemize}
	\item  Designed and Developed backend API following client requirements.
	\vspace*{-.5em}
	\item  Server Maintenance  and Bug fixing.
	\vspace*{-.5em}
\end{itemize}

\hangpara{1.5em}{1}
{\sl \textbf{\href{https://www.grp.gov.bd/}{Government Resource Planning(GRP)} }}   \\
	Micro Service Based ERP system managing all the government departments resources. \\
{\sl Technology:} {\sl Java Spring Boot \& Angular 8
	\vspace*{-.6em}	
\begin{itemize}
	\item  Design and Developed Two Module (Meeting and Event) out of Nine Modules from scratch.
	\vspace*{-.5em}
	\item  Designed intercommunication scheme between different module.
	\vspace*{-.5em}
	\item  Worked with clustered database, Message Queues, Elastic Stack etc.
		\vspace*{-.5em}
	\item  Used Docker, Jenkins tools for continuous integration and deployment. 
			\vspace*{-.5em}
\end{itemize}

\hangpara{1.5em}{1}
{\sl \textbf{\href{https://nile.ch/}{Nile} }}   \\
A online shopping platform for branded Cloths produced by NILE company.\\
{\sl Technology:} {\sl Ruby On Rails, HTML, Sass, JavaScript.
	\vspace*{-.6em}
	\begin{itemize}
		\item  Developed several new features and customized existing functionalities.
		\vspace*{-.5em}
		\item Migrate Data from old structured Database(Mysql) to New structured  Database(PostGresql).
		\vspace*{-.5em}
		\item  Bug fixing.
	\end{itemize}	
	
	\vspace*{-.5em}
\hangpara{1.5em}{1}
{\sl \textbf{\href{https://biyeta.com/en}{Biyeta} }}   \\
One of the popular matrimony sites of Bangladesh \\
{\sl Technology:} {\sl Ruby On Rails, HTML, Sass, JavaScript.
		\vspace*{-.6em}
\begin{itemize}
	\item  Developed several API to be used by the mobile application.
		\vspace*{-.5em}
	\item  Optimized the matching algorithm used to find match.
		\vspace*{-.5em}
	\item  Bug fixing and feature extension.
\end{itemize}
	
\hangpara{1.5em}{1}
{\sl \textbf{\href{https://snapknot.com/}{SnapKnot} }}   \\
A platform searching and connecting the best photographers across USA \\
{\sl Technology:} {\sl Ruby On Rails, HTML, Sass, JavaScript.
		\vspace*{-.6em}
	\begin{itemize}
		\item  Developed several new features and customized existing functionalities.
		\vspace*{-.5em}
		\item Modified the subscription and payment system of the application. 
		\vspace*{-.5em}
		\item Server maintaining and Application deployment. 
		\vspace*{-.5em}
		\item  Bug fixing.
	\end{itemize}


\hangpara{1.5em}{1}
{\sl \textbf{\href{https://brokerpro.com/}{BrokerPro} }}   \\
Transportation management system available in USA\\
{\sl Technology:} {\sl Ruby On Rails, HTML, Sass, JavaScript.	
		\vspace*{-.6em}	
  	\begin{itemize}
  	\item  Developed several new features and customized existing functionalities.
  	\vspace*{-.5em}
  	\item Server maintaining and Application deployment. 
  	\vspace*{-.5em}
  	\item  Bug fixing.
  \end{itemize}
  
\vspace{-18pt}
\section*{Reviewer Activity}
\vspace{-20pt}
\noindent\makebox[\linewidth]{\rule{500pt}{1.8pt}}  
  
\hangpara{1.5em}{1}
{\sl \textbf{International Journal of Computers and Applications }} \hfill   2018$-$ Present\\
{\sl Role:} Reviewer  \\

\vspace*{-1.8em}	
\hangpara{1.5em}{1}
{\sl \textbf{Annals of Data Science (AODS)  }} \hfill   2019$-$ Present\\
{\sl Role:} Reviewer  \\

\vspace*{-1.8em}
\hangpara{1.5em}{1}
{\sl \textbf{SGIoT 2018 }} \hfill   2018\\
{\sl Role:} WORKSHOP TRACK ATBD 2018 - REVIEWER  \\
  
  
 \vspace{-28pt}
\section*{Skills}
\vspace{-20pt}
\noindent\makebox[\linewidth]{\rule{500pt}{1.8pt}}    
\begin{itemize}
	\item \textbf{DevOps}: \space Docker, Vagrant, Jenkins, CircleCI, Ansible
		\vspace*{-.5em}
	\item \textbf{Back-end}: \space Ruby on Rails, Spring Boot, Django, REST API
	\vspace*{-.5em}
	\item \textbf{Front-end}: Angular 8, HTML5, SASS, React Js
	\vspace*{-.5em}
	\item \textbf{Programming Languages}: Ruby, Python, JAVA, LaTeX, R, Shell Script, C, C++ 
	\vspace*{-.5em}
	\item \textbf{Operating System}: Windows, Linux, Mac\\

\end{itemize}
  
 
 \vspace{-27pt}
 \section*{Extracurricular Activity}
 \vspace{-20pt}
 \noindent\makebox[\linewidth]{\rule{500pt}{1.8pt}}  
	\begin{itemize}
	\item  Organizing committee Member of 7th IUT ICT FEST 2015
	\vspace*{-.7em}
	\item Volunteer during 6th, 5th and 4th IUT ICT FEST (2012,2013,2014)

\end{itemize}  
  
  
\end{document}
